---
title: "Business Intelligence Lab Submission Markdown"
author: "<Knights>"
date: "<4/10/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, class group (just the letter; A, B, or C), and ID per line, e.g., 123456 - A - John Leposo; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  135230 - B - Peter Aringo                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  135356 - B - Ann Kigera                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  ID - Class Group - Name                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  ID - Class Group - Name                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 5.  ID - Class Group - Name                                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | *\<knights\>*                                                                                                       |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## formatR - Required to format R code in the markdown ----
if (!is.element("formatR", installed.packages()[, 1])) {
  install.packages("formatR", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("formatR")


## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("readr")
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading the Student Performance Dataset

The 20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset is then loaded. The dataset and its metadata are available here: <https://drive.google.com/drive/folders/1-BGEhfOwquXF6KKXwcvrx7WuZXuqmW9q?usp=sharing>

```{r Load Dataset}
student_performance_dataset <-
  readr::read_csv(
                  "../data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.CSV", # nolint
                  col_types =
                  readr::cols(
                              class_group =
                              readr::col_factor(levels = c("A", "B", "C")),
                              gender = readr::col_factor(levels = c("1", "0")),
                              YOB = readr::col_date(format = "%Y"),
                              regret_choosing_bi =
                              readr::col_factor(levels = c("1", "0")),
                              drop_bi_now =
                              readr::col_factor(levels = c("1", "0")),
                              motivator =
                              readr::col_factor(levels = c("1", "0")),
                              read_content_before_lecture =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              anticipate_test_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              answer_rhetorical_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              find_terms_I_do_not_know =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              copy_new_terms_in_reading_notebook =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              take_quizzes_and_use_results =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              reorganise_course_outline =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              write_down_important_points =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              space_out_revision =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              studying_in_study_group =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              schedule_appointments =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              goal_oriented =
                              readr::col_factor(levels =
                                                c("1", "0")),
                              spaced_repetition =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              testing_and_active_recall =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              interleaving =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              categorizing =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              retrospective_timetable =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              cornell_notes =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              sq3r = readr::col_factor(levels =
                                                       c("1", "2", "3", "4")),
                              commute = readr::col_factor(levels =
                                                          c("1", "2",
                                                            "3", "4")),
                              study_time = readr::col_factor(levels =
                                                             c("1", "2",
                                                               "3", "4")),
                              repeats_since_Y1 = readr::col_integer(),
                              paid_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              free_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              extra_curricular = readr::col_factor(levels =
                                                                   c("0", "1")),
                              sports_extra_curricular =
                              readr::col_factor(levels = c("0", "1")),
                              exercise_per_week = readr::col_factor(levels =
                                                                    c("0", "1",
                                                                      "2",
                                                                      "3")),
                              meditate = readr::col_factor(levels =
                                                           c("0", "1",
                                                             "2", "3")),
                              pray = readr::col_factor(levels =
                                                       c("0", "1",
                                                         "2", "3")),
                              internet = readr::col_factor(levels =
                                                           c("0", "1")),
                              laptop = readr::col_factor(levels = c("0", "1")),
                              family_relationships =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              friendships = readr::col_factor(levels =
                                                              c("1", "2", "3",
                                                                "4", "5")),
                              romantic_relationships =
                              readr::col_factor(levels =
                                                c("0", "1", "2", "3", "4")),
                              spiritual_wellnes =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              financial_wellness =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              health = readr::col_factor(levels = c("1", "2",
                                                                    "3", "4",
                                                                    "5")),
                              day_out = readr::col_factor(levels = c("0", "1",
                                                                     "2", "3")),
                              night_out = readr::col_factor(levels = c("0",
                                                                       "1", "2",
                                                                       "3")),
                              alcohol_or_narcotics =
                              readr::col_factor(levels = c("0", "1", "2", "3")),
                              mentor = readr::col_factor(levels = c("0", "1")),
                              mentor_meetings = readr::col_factor(levels =
                                                                  c("0", "1",
                                                                    "2", "3")),
                              `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                              readr::col_factor(levels = c("0", "1")),
                              GRADE = readr::col_factor(levels =
                                                        c("A", "B", "C", "D",
                                                          "E"))),
                  locale = readr::locale())
```

## Description of the Dataset

We then display the number of observations and number of variables. We have 101 observations and 100 variables to work with.

```{r Your Fourth Code Chunk}
dim(student_performance_dataset)
```

Next, we display the quartiles for each numeric variable[*... think of this process as **"storytelling using the data."** Tell us what is happening; tell us what you are discovering as you proceed with the markdown; walk us through your code step-by-step (a code walkthrough).*]{#highlight style="color: blue"}

```{r Your Fifth Code Chunk}
summary(student_performance_dataset)
```

# \<You can Provide Another Appropriate Title Here if you wish\>

Describe the code chunk here.
This R code chunk operates on a student performance dataset, initially transforming and summarizing the data by creating a new gender variable, selecting relevant columns, filtering out missing data, grouping by class and gender, and calculating average evaluation ratings. This process facilitates the analysis of course evaluation ratings across various class groups and genders. Additionally, the code generates two forms of output. First, it produces a styled HTML table with column renaming, colour-coded ratings, and Bootstrap styling for better presentation. Second, it creates a visual bar chart using ggplot2, displaying average ratings by class group and gender with distinct colours and a customized theme. These visualizations offer a comprehensive and visually appealing way to explore and compare course evaluation ratings, enhancing the overall accessibility and informativeness of the dataset.


```{r Your Sixth Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
evaluation_per_group_per_gender <- student_performance_dataset %>% # nolint
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  select(class_group, gender,
         `Student's Gender`, `Average Course Evaluation Rating`) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  group_by(class_group, `Student's Gender`) %>%
  summarise(average_evaluation_rating =
              mean(`Average Course Evaluation Rating`)) %>%
  arrange(desc(average_evaluation_rating), .by_group = TRUE)

# Decorated tabular output
evaluation_per_group_per_gender %>%
  rename(`Class Group` = class_group) %>%
  rename(`Average Course Evaluation Rating` = average_evaluation_rating) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`) %>%
  mutate(`Average Course Evaluation Rating` =
           color_tile("#B9BCC2", "#536CB5")
           (`Average Course Evaluation Rating`)) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Course Evaluation Rating per Group and per Gender") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
# Decorated visual bar chart
evaluation_per_group_per_gender %>%
  ggplot() +
  geom_bar(aes(x = class_group, y = average_evaluation_rating,
               fill = `Student's Gender`),
           stat = "identity", position = "dodge") +
  expand_limits(y = 0) +
  blue_grey_theme() +
  scale_fill_manual(values = blue_grey_colours_2) +
  ggtitle("Course Evaluation Rating per Group and per Gender") +
  labs(x = "Class Group", y = "Average Rating")


```

## \<You Can Have a Sub-Title Here if you wish\>

Describe the code chunk here.

The provided R code defines a function called expand_contractions, which takes a text document as input and expands common contractions within the text. It uses the gsub function to replace contractions like "I'm" with "I am," "you're" with "you are," and so on, making the text more explicit and suitable for natural language processing or text analysis tasks. The function is case-insensitive, ensuring it works for contractions in both uppercase and lowercase forms, and it's particularly useful for preprocessing text data for various linguistic analyses.

```{r Your Seventh Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

```

## \<You Can Have Another Sub-Title Here if you wish\>

Describe the code chunk here.

```{r Your Eighth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
```

**etc.** as per the lab submission requirements. Be neat and communicate in a clear and logical manner.
